### 2019-09-24 source/cadabra/tests/semantic/dRabcd.tex
Initial commit
This is where it all begins ...

   term00A = cdblib.get ('check000','expected/dGamma.json')
   term01A = cdblib.get ('check001','expected/dGamma.json')
   term02A = cdblib.get ('check002','expected/dGamma.json')
   term03A = cdblib.get ('check003','expected/dGamma.json')
   term04A = cdblib.get ('check004','expected/dGamma.json')

   term00B = cdblib.get ('check000','output/dGamma.json')
   term01B = cdblib.get ('check001','output/dGamma.json')
   term02B = cdblib.get ('check002','output/dGamma.json')
   term03B = cdblib.get ('check003','output/dGamma.json')
   term04B = cdblib.get ('check004','output/dGamma.json')

>>>>

   term00A = cdblib.get ('check000','expected/dRabcd.json')
   term01A = cdblib.get ('check001','expected/dRabcd.json')
   term02A = cdblib.get ('check002','expected/dRabcd.json')
   term03A = cdblib.get ('check003','expected/dRabcd.json')
   term04A = cdblib.get ('check004','expected/dRabcd.json')

   term00B = cdblib.get ('check000','output/dRabcd.json')
   term01B = cdblib.get ('check001','output/dRabcd.json')
   term02B = cdblib.get ('check002','output/dRabcd.json')
   term03B = cdblib.get ('check003','output/dRabcd.json')
   term04B = cdblib.get ('check004','output/dRabcd.json')

### 2019-09-24 source/cadabra/tests/semantic/gen2rnc.tex
Initial commit
This is where it all begins ...

   term00A = cdblib.get ('check000','expected/dRabcd.json')
   term01A = cdblib.get ('check001','expected/dRabcd.json')
   term02A = cdblib.get ('check002','expected/dRabcd.json')
   term03A = cdblib.get ('check003','expected/dRabcd.json')
   term04A = cdblib.get ('check004','expected/dRabcd.json')

   term00B = cdblib.get ('check000','output/dRabcd.json')
   term01B = cdblib.get ('check001','output/dRabcd.json')
   term02B = cdblib.get ('check002','output/dRabcd.json')
   term03B = cdblib.get ('check003','output/dRabcd.json')
   term04B = cdblib.get ('check004','output/dRabcd.json')

>>>>

   term00A = cdblib.get ('check000','expected/gen2rnc.json')
   term01A = cdblib.get ('check001','expected/gen2rnc.json')
   term02A = cdblib.get ('check002','expected/gen2rnc.json')
   term03A = cdblib.get ('check003','expected/gen2rnc.json')
   term04A = cdblib.get ('check004','expected/gen2rnc.json')

   term00B = cdblib.get ('check000','output/gen2rnc.json')
   term01B = cdblib.get ('check001','output/gen2rnc.json')
   term02B = cdblib.get ('check002','output/gen2rnc.json')
   term03B = cdblib.get ('check003','output/gen2rnc.json')
   term04B = cdblib.get ('check004','output/gen2rnc.json')

### 2019-09-24 source/cadabra/tests/semantic/geodesic-ivp.tex
Initial commit
This is where it all begins ...

   term00A = cdblib.get ('check000','expected/connection.json')
   term01A = cdblib.get ('check001','expected/connection.json')
   term02A = cdblib.get ('check002','expected/connection.json')
   term03A = cdblib.get ('check003','expected/connection.json')
   term04A = cdblib.get ('check004','expected/connection.json')
   term05A = cdblib.get ('check005','expected/connection.json')

   term00B = cdblib.get ('check000','output/connection.json')
   term01B = cdblib.get ('check001','output/connection.json')
   term02B = cdblib.get ('check002','output/connection.json')
   term03B = cdblib.get ('check003','output/connection.json')
   term04B = cdblib.get ('check004','output/connection.json')
   term05B = cdblib.get ('check005','output/connection.json')

>>>>

   term00A = cdblib.get ('check000','expected/geodesic-ivp.json')
   term01A = cdblib.get ('check001','expected/geodesic-ivp.json')
   term02A = cdblib.get ('check002','expected/geodesic-ivp.json')
   term03A = cdblib.get ('check003','expected/geodesic-ivp.json')
   term04A = cdblib.get ('check004','expected/geodesic-ivp.json')
   term05A = cdblib.get ('check005','expected/geodesic-ivp.json')

   term00B = cdblib.get ('check000','output/geodesic-ivp.json')
   term01B = cdblib.get ('check001','output/geodesic-ivp.json')
   term02B = cdblib.get ('check002','output/geodesic-ivp.json')
   term03B = cdblib.get ('check003','output/geodesic-ivp.json')
   term04B = cdblib.get ('check004','output/geodesic-ivp.json')
   term05B = cdblib.get ('check005','output/geodesic-ivp.json')

### 2019-09-24 source/cadabra/tests/semantic/geodesic-lsq.tex
Initial commit
This is where it all begins ...

   term00A = cdblib.get ('check000','expected/geodesic-ivp.json')
   term01A = cdblib.get ('check001','expected/geodesic-ivp.json')
   term02A = cdblib.get ('check002','expected/geodesic-ivp.json')
   term03A = cdblib.get ('check003','expected/geodesic-ivp.json')
   term04A = cdblib.get ('check004','expected/geodesic-ivp.json')
   term05A = cdblib.get ('check005','expected/geodesic-ivp.json')

   term00B = cdblib.get ('check000','output/geodesic-ivp.json')
   term01B = cdblib.get ('check001','output/geodesic-ivp.json')
   term02B = cdblib.get ('check002','output/geodesic-ivp.json')
   term03B = cdblib.get ('check003','output/geodesic-ivp.json')
   term04B = cdblib.get ('check004','output/geodesic-ivp.json')
   term05B = cdblib.get ('check005','output/geodesic-ivp.json')

>>>>

   term00A = cdblib.get ('check000','expected/geodesic-lsq.json')
   term01A = cdblib.get ('check001','expected/geodesic-lsq.json')
   term02A = cdblib.get ('check002','expected/geodesic-lsq.json')
   term03A = cdblib.get ('check003','expected/geodesic-lsq.json')
   term04A = cdblib.get ('check004','expected/geodesic-lsq.json')
   term05A = cdblib.get ('check005','expected/geodesic-lsq.json')

   term00B = cdblib.get ('check000','output/geodesic-lsq.json')
   term01B = cdblib.get ('check001','output/geodesic-lsq.json')
   term02B = cdblib.get ('check002','output/geodesic-lsq.json')
   term03B = cdblib.get ('check003','output/geodesic-lsq.json')
   term04B = cdblib.get ('check004','output/geodesic-lsq.json')
   term05B = cdblib.get ('check005','output/geodesic-lsq.json')

### 2019-09-24 source/cadabra/tests/semantic/metric.tex
Initial commit
This is where it all begins ...

   term00A = cdblib.get ('check000','expected/metric-inv.json')
   term01A = cdblib.get ('check001','expected/metric-inv.json')
   term02A = cdblib.get ('check002','expected/metric-inv.json')
   term03A = cdblib.get ('check003','expected/metric-inv.json')
   term04A = cdblib.get ('check004','expected/metric-inv.json')
   term05A = cdblib.get ('check005','expected/metric-inv.json')
   term06A = cdblib.get ('check005','expected/metric-inv.json')
   term07A = cdblib.get ('check005','expected/metric-inv.json')

   term00B = cdblib.get ('check000','output/metric-inv.json')
   term01B = cdblib.get ('check001','output/metric-inv.json')
   term02B = cdblib.get ('check002','output/metric-inv.json')
   term03B = cdblib.get ('check003','output/metric-inv.json')
   term04B = cdblib.get ('check004','output/metric-inv.json')
   term05B = cdblib.get ('check005','output/metric-inv.json')
   term06B = cdblib.get ('check005','output/metric-inv.json')
   term07B = cdblib.get ('check005','output/metric-inv.json')

>>>>

   term00A = cdblib.get ('check000','expected/metric.json')
   term01A = cdblib.get ('check001','expected/metric.json')
   term02A = cdblib.get ('check002','expected/metric.json')
   term03A = cdblib.get ('check003','expected/metric.json')
   term04A = cdblib.get ('check004','expected/metric.json')
   term05A = cdblib.get ('check005','expected/metric.json')
   term06A = cdblib.get ('check005','expected/metric.json')
   term07A = cdblib.get ('check005','expected/metric.json')

   term00B = cdblib.get ('check000','output/metric.json')
   term01B = cdblib.get ('check001','output/metric.json')
   term02B = cdblib.get ('check002','output/metric.json')
   term03B = cdblib.get ('check003','output/metric.json')
   term04B = cdblib.get ('check004','output/metric.json')
   term05B = cdblib.get ('check005','output/metric.json')
   term06B = cdblib.get ('check005','output/metric.json')
   term07B = cdblib.get ('check005','output/metric.json')

   # bug: can't push this function into shared.py
   #      no synatx error, but cadabra doesn't cancel equal terms
   # see ~/cadabra/bugs/bug02

   def check (objA,objB):
       tmp := @(objA) - @(objB).
       distribute         (tmp)
       tmp = shared.standard_indices (tmp)
       tmp = shared.product_sort (tmp)
       rename_dummies     (tmp)
       canonicalise       (tmp)

       return tmp

### 2019-09-24 source/cadabra/tests/semantic/rnc2gen.tex
Initial commit
This is where it all begins ...

   term00A = cdblib.get ('check000','expected/gen2rnc.json')
   term01A = cdblib.get ('check001','expected/gen2rnc.json')
   term02A = cdblib.get ('check002','expected/gen2rnc.json')
   term03A = cdblib.get ('check003','expected/gen2rnc.json')
   term04A = cdblib.get ('check004','expected/gen2rnc.json')

   term00B = cdblib.get ('check000','output/gen2rnc.json')
   term01B = cdblib.get ('check001','output/gen2rnc.json')
   term02B = cdblib.get ('check002','output/gen2rnc.json')
   term03B = cdblib.get ('check003','output/gen2rnc.json')
   term04B = cdblib.get ('check004','output/gen2rnc.json')

>>>>

   term00A = cdblib.get ('check000','expected/rnc2gen.json')
   term01A = cdblib.get ('check001','expected/rnc2gen.json')
   term02A = cdblib.get ('check002','expected/rnc2gen.json')
   term03A = cdblib.get ('check003','expected/rnc2gen.json')
   term04A = cdblib.get ('check004','expected/rnc2gen.json')

   term00B = cdblib.get ('check000','output/rnc2gen.json')
   term01B = cdblib.get ('check001','output/rnc2gen.json')
   term02B = cdblib.get ('check002','output/rnc2gen.json')
   term03B = cdblib.get ('check003','output/rnc2gen.json')
   term04B = cdblib.get ('check004','output/rnc2gen.json')

### 2019-09-24 source/cadabra/tests/semantic/rnc2rnc.tex
Initial commit
This is where it all begins ...

   term00A = cdblib.get ('check000','expected/rnc2gen.json')
   term01A = cdblib.get ('check001','expected/rnc2gen.json')
   term02A = cdblib.get ('check002','expected/rnc2gen.json')
   term03A = cdblib.get ('check003','expected/rnc2gen.json')
   term04A = cdblib.get ('check004','expected/rnc2gen.json')

   term00B = cdblib.get ('check000','output/rnc2gen.json')
   term01B = cdblib.get ('check001','output/rnc2gen.json')
   term02B = cdblib.get ('check002','output/rnc2gen.json')
   term03B = cdblib.get ('check003','output/rnc2gen.json')
   term04B = cdblib.get ('check004','output/rnc2gen.json')

>>>>

   term00A = cdblib.get ('check000','expected/rnc2rnc.json')
   term01A = cdblib.get ('check001','expected/rnc2rnc.json')
   term02A = cdblib.get ('check002','expected/rnc2rnc.json')
   term03A = cdblib.get ('check003','expected/rnc2rnc.json')
   term04A = cdblib.get ('check004','expected/rnc2rnc.json')

   term00B = cdblib.get ('check000','output/rnc2rnc.json')
   term01B = cdblib.get ('check001','output/rnc2rnc.json')
   term02B = cdblib.get ('check002','output/rnc2rnc.json')
   term03B = cdblib.get ('check003','output/rnc2rnc.json')
   term04B = cdblib.get ('check004','output/rnc2rnc.json')
